\documentclass[../main.tex]{subfiles}
\begin{document}
	\chapter{Theorem and proof} \label{ch:proof}
\noindent  The work revolves around the following theorem and its proof. 
	\section{Theorem}
	\begin{theorem} Let $ \sigma \in  \mathcal{M}$. Set
		$$ \Sigma_n = span\{\sigma(w\cdot x + \theta) : w\in \mathbb{R}^n, \theta \in \mathbb{R} \}$$
		Then $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$ if and only if $\sigma$ is not a polynomial. 
	
	\end{theorem}


\subsection{Previous results}
\noindent Previous research on the approximation capabilities of feedforward networks can be found. These studies show that if the network's activation functions obey an explicit set of assumptions then the network can indeed be shown to be a universal approximator. For example \cite{HORNIK1991251}  has proven two general results, as follows:

\begin{theorem} (Hornik Theorem 1). Multilayer feedforward networks with a bounded and nonconstant activation function can approximate any function in $L^p(\mu)$ arbitrary well, given a sufficiently large number of hidden units. 
\end{theorem}

\begin{theorem} (Hornik Theorem 2) Multilayer feedforward networks with a continuous, bounded and nonconstant activation function can approximate any continuous function on $X$ arbitrarily well (with respect to the uniform distance) given a sufficiently large number of hidden units. 
\end{theorem}

\noindent
The theorem generalizes Hornik's Theorem 2 by establishing necessary and sufficient conditions for universal approximation. Note that the theorem merely requires "nonpolynomiality" in the activation function. Unlike Hornik's result, the activation functions do not need to be continuous or smooth. This has an important biological interpretation because the activation functions of real neurons may well be discontinuous or even non-elementary.

	\section{Proof}
	\subsection{If $\sigma$ is not a polynomial then $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$ }
	\noindent Consider that $\sigma$ is not an algebraic polynomial and we aim to show that $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$. In order to show that, we need to following Lemmas. \\ \\
	%\subsubsection{$\sigma$ is not a polynomial $\Rightarrow $ $\sigma \ast \varphi$ is not a polynomial.}
	\begin{lema}  % L1 :step 6
		If we have that $\sigma \ast \varphi $ is a polynomial for all $\varphi \in \mathcal{C}^\infty_0 $, then the degree of the polynomial $\sigma \ast \varphi $ is finite, i.e. there exists an $m$ $\in \mathbb{N}$ such that $ deg (\sigma \ast \varphi) \leq m$ for all $\varphi \in \mathcal{C}^\infty_0$. 
	\end{lema}
	\begin{proof}
		We first prove the claim in the case of $\varphi \in \mathcal{C}^\infty_0[a,b]$, for some $a<b$. \\ \\ By Proposition \ref{prop:frech} we have that $(\mathcal{C}^\infty_0[a,b],\rho)$ is a complete metric space.  \\ \\  Consider the following set, \\ $$V_k= \{\varphi \in \mathcal{C}_0^\infty[a,b] \, | \,  deg(\sigma \ast \varphi ) \leq k\}.$$ \\ 
		We want to show that $\mathcal{C}_0^\infty[a,b] \subseteq V_k.$ \\ \\ \\ \\ The set $ V_k$ fulfills the following properties: $V_k \subset V_{k+1}$, $V_k $ is a closed subspace and $\cup_{k=0}^\infty V_k = \mathcal{C}_0^\infty[a,b]$. \\ \\ 
	\noindent As $\mathcal{C}_0^\infty[a,b]$ is a complete metric space, by Baire's Category Theorem \ref{baire}, this set is of category $II$, i.e. $\mathcal{C}_0^\infty[a,b]$  cannot be written as a countable union of nowhere-dense sets. Recall that $\mathcal{C}_0^\infty[a,b]$ can be written as a countable union of $V_k$ $\mathcal{C}_0^\infty[a,b]=\cup_{k=0}^\infty V_k$, therefore some $V_m $ is not a nowhere-dense set, that is, there exists an open set $U$ of $ C_0^\infty[a,b]$ that is contained in the closure of $V_m$, but, as $V_m$ is closed, we have that $U$ is contained in $V_m$. Therefore, some $V_m$ contains a nonempty open set.  By results in topology, any open set of a vector space contains a basis of the vector space, therefore 	$V_m$ is a vector space thus $V_m=\mathcal{C}_0^\infty[a,b]$. \\ 
		
		\noindent For the general case where $\varphi \in \mathcal{C}_0^\infty$, we note that the number $m$ does not depend on the interval $[a,b]$. This can be seen as follows. By translation $m$ depends at most of the length of the interval. Let $[A,B]$ be any interval. For $\varphi \in \mathcal{C}^\infty_0[A,B]$ we can find $\varphi_i \in \mathcal{C}^\infty_0[a_i,b_i]$ for $i=1,...,k$ such that $[A,B] \subset \cup_{i=1}^k[a_i,b_i]$ where $b_i -a_i =b-a$ and $\varphi=\sum_{i=1}^k \varphi_i$ Thus $$\sigma \ast \varphi = \sum_{i=1}^k \sigma \ast \varphi_i$$ and for every $i=1,...,k $ we have that $\sigma \ast \varphi$ is a polynomial of degree less than or equal to m. Therefore $deg(\sigma \ast \varphi) \leq m$.
	\end{proof}
	\begin{lema} % L2: step 7
		If $\sigma \ast \varphi$ is a polynomial such that $ deg (\sigma \ast \varphi) \leq m$ for all $\varphi \in \mathcal{C}^\infty_0$, then $\sigma$ is a polynomial of degree at most $m$. 
	\end{lema}
	\begin{proof} 
	If $\sigma \ast \varphi$ is a polynomial of degree $m$.
	For all $\varphi \in \mathcal{C}^\infty_0$, using (\ref{prop:2}) we have that
	$$(\sigma \ast \varphi)^{(m+1)} \, (x)=\int \sigma(x-y)\varphi^{(m+1)}(y) \, dy= 0$$  
	From standard results in Distribution Theory \textcolor{red}{aqui vam dir de ficar nomes la referencia}[e.g., Friedman(1963, 57-59)], $\sigma $ is itself a polynomial of degree at most $m$ (a.e.).
	\end{proof} 

\begin{prop}
If $\sigma$ is not a polinomial then $\sigma \ast \varphi$ is not a polynomial for some $\varphi \in \mathcal{C}^\infty_0$. 
\end{prop}
\begin{proof}
We will show the contrapositive. Suppose that the convolution $\sigma \ast \varphi$ is a polynomial for all $\varphi \in \mathcal{C}^\infty_0$, by Lemma 1 the degree of the convolution is finite. Now we have that $\sigma \ast \varphi$ is a polynomial of finite degree, by Lemma 2 we have that $\sigma$ is a polynomial. 
\end{proof}

%\subsubsection{$\sigma \ast \varphi \in \overline{\Sigma_1}$}
	\begin{lema} % L3: step 4
		For each $\varphi \in  \mathcal{C}^\infty_0$, $ \sigma \ast \varphi \in  \overline{\Sigma_1}$. 
		
	\end{lema}
	
	\begin{proof} % proof step 4
		We recall that set 
		\begin{equation}
			\Sigma_1 = \text{span} \{ {\sigma(w\cdot x + \theta) : w\in \mathbb{R}, \theta \in \mathbb{R} \} } 
			\tag{1}
			%\label{eq:ecuacion1}
		\end{equation}
		Consider $$h_m= \sum_{i=1}^m\varphi(y_i)\Delta y_i \sigma(x-y_i)$$ 
		The sequence $(h_m)$ satisfies $h_j\in \Sigma_1$ for $j=1,...,m$. ($w_i=1,\theta_i=-y_i, \beta_i=\varphi(y_i)\Delta y_i$).\\ \\ 
		Where $y_i=-\alpha + \frac{2i\alpha}{m}$, $\Delta y_i=\frac{2\alpha}{m}$ for $i=1,...,m$. Partition of the interval $[-\alpha,\alpha]$ \\ \\ We want to show that $h_m \rightrightarrows \sigma \ast \varphi $ in $[-\alpha,\alpha]$.  \\ \\
		Given $\epsilon >0$, we choose $\delta >0$ such that $$10\delta \| \sigma\|_{L^\infty\{-2\alpha,2\alpha\}}\|\varphi \|_{L^\infty} \leq \frac{\epsilon}{3}$$ Note that ... \\ \\ 
		We know that $\sigma \in M$. Hence, for this given $\delta>0$ and $[-\alpha,\alpha]$ interval, there exists $r(\delta)$ finite number of intervals the measure of whose union $\mathscr{U}$ is $\delta$ such that $\sigma$ is uniformly continuous on $[-2\alpha,2\alpha]$. We now choose $m_i$ sufficiently large so that
		\begin{enumerate}
			\item $m_1 \delta > \alpha r(\delta)$. We can do this by Archimedes' principle.
			\item From the uniform continuity of $\varphi$. 
			
			If $|s-t| \leq \frac{2 \alpha }{m_2}$ then $$|\varphi(s)- \varphi(t)| \leq \frac{\epsilon}{2 \alpha \| \sigma\|_{L^\infty[-2\alpha,2\alpha]}}$$
			
			\item From the previous, $\sigma$ is uniformly continuous on  $[-2\alpha,2\alpha]/ U$. We chose m such that, if $s,t \in [-2\alpha, 2\alpha]/U$ and $|s-t|\leq \frac{2\alpha}{m_3}$ then $$|\sigma(s)-\sigma(t)| \leq \frac{\epsilon}{\|\varphi\|_L}$$
		\end{enumerate}
		We choose $m$ such that $m=max\{m_1,m_2,m_3\}$. \\ \\ 
		Now, fix $x\in [-\alpha,\alpha] $. Set $\Delta_i= [y_{i-1},y_i]$ where $y_0= \alpha$. \\ \\
		First, recall that,\\
		$$\int \sigma(x-y)\varphi(y)dy = \sum_{i=1}^m \int_{\Delta_i}\sigma(x-y)\varphi(y)dy$$
		Consider the following difference 

\begin{equation*} 
	\begin{split}
		\Bigg| \int \sigma(x-y)\varphi(y)dy -  \sum_{i=1}^m \int_{\Delta_i}& \sigma(x-y_i) \varphi(y)dy \Bigg|  \\
		& = \left|  \sum_{i=1}^m \int_{\Delta_i}\sigma(x-y)\varphi(y)dy -  \sum_{i=1}^m \int_{\Delta_i}\sigma(x-y_i)\varphi(y)dy \right|  \\
		& =  \left|  \sum_{i=1}^m \int_{\Delta_i}\varphi(y)\Big( \sigma(x-y) - \sigma(x-y_i)\Big)dy \right| \\
		&\leq  \sum_{i=1}^m \int_{\Delta_i} \left| \varphi(y)\right| \left| \sigma(x-y)-\sigma(x-y_i)\right|dy 
	\end{split}
\end{equation*}
		If $x-\Delta_i \cap U = \varnothing $. Since $x-y \notin U$ , $x-y_i \notin U$ and $x-y_i \in [-2\alpha,2\alpha]$. For choice of $m$ in property 2, we have\\ 
		\begin{equation*}
			\begin{split}
				\sum_{i=1}^m  \int_{\Delta_i} \left| \varphi(y)\right| \left| \sigma(x-y)-\sigma(x-y_i)\right|dy  \leq  \frac{\epsilon}{\| \varphi\|_{L_1}}  \sum_{i=1}^m  \int_{\Delta_i} \left| \varphi(y)\right| & \\
				& =  \frac{\epsilon}{3\| \varphi\|_{L_1}} \int \left|\varphi(y)\right| dy \\
				& =  \frac{\epsilon}{3\| \varphi\|_{L_1}} \left|\varphi(y)\right|_{L_1}  \\
				& = \frac{\epsilon}{3} 
			\end{split}
		\end{equation*}
		\\ 
		\noindent If $x-\Delta_i \cap U \neq \varnothing$\\ \\ 
		$\sum_i |\tilde{\Delta_i}| = \sum_i|(x-\Delta_i \cap U)| \leq |U|+2|\Delta_i| r(\delta) \leq \delta + 2 \cdot \frac{2\alpha}{m} r(\delta) \leq \delta +4\delta = 5\delta$  \\ \\ 
		True by our choice of m, satisfies $m\delta > \alpha r(\delta) \iff \delta > \frac{\alpha \cdot r(\delta)}{m}$
		
		
		\begin{equation*}
			\begin{split}
				\sum_{i=1}^m  \int_{\tilde{\Delta_i}} \left| \varphi(y)\right| \left| \sigma(x-y)-\sigma(x-y_i)\right|dy & \\
				&  \leq  \sum_{i=1}^m  \int_{\tilde{\Delta_i}} \| \varphi\|_{L^{\infty}} \, 2 \| \sigma \|_{L^{\infty}[-2\alpha,2\alpha]} \\
				& = \| \varphi\|_{L^{\infty}} \, 2 \| \sigma \|_{L^{\infty}[-2\alpha,2\alpha]} \sum_i| \tilde{\Delta_i} | \\
				& \leq \| \varphi\|_{L^{\infty}} \, 2 \| \sigma \|_{L^{\infty}[-2\alpha,2\alpha]} \, 5 \delta \leq \epsilon /3
			\end{split}
		\end{equation*}

\begin{equation*} 
	\begin{split}
		\Bigg| \sum_{i=1}^m \int_{\Delta_i} \sigma(x-y_i)\varphi(y)dy -  \sum_{i=1}^m \sigma(x-y_i)& \varphi(y_i)\Delta y_i \Bigg| \\
		& =  \left|  \sum_{i=1}^m \int_{\Delta_i} \sigma(x-y_i) [\varphi(y)-\varphi(y_i)] dy \right| \\
		& \leq  \sum_{i=1}^m \int_{\Delta_i}  \left| \sigma(x-y_i)\right| \left| \varphi(y) - \varphi(y_i)\right|dy  \\
		& \leq  \sum_{i=1}^m \int_{\Delta_i}  \left| \sigma(x-y_i)\right| dy \left[ \frac{\epsilon/3}{2\alpha \| \sigma\|_{L^\infty[-2\alpha,2\alpha]}}\right]  \leq \frac{\epsilon}{3} 
	\end{split}
\end{equation*}
Finally, we have the result $h_m \rightrightarrows \sigma \ast \varphi $ because

$$\Bigg| \int \sigma(x-y)\varphi(y)dy -  \sum_{i=1}^m \sigma(x-y_i) \varphi(y_i) \Delta y_i \Bigg| \leq \epsilon $$
for all $x\in [-\alpha,\alpha ]$
	\end{proof}
	
	%\subsubsection{$\Sigma_1$ dense in $\mathcal{C}(\mathbb{R})$}
	\begin{lema} % L4: step 3
		If $\sigma \in \mathcal{C}^{\infty}$, then $ \Sigma_1$ is dense in  $\mathcal{C}(\mathbb{R})$.
	\end{lema}
	
	\begin{proof} % proof step 3
		We suppose that  $\sigma \in \mathcal{C}^{\infty}$ and recall by the theorem hypothesis $\sigma$ is not a polynomial. 
		 We can write any function $f$ of the set $\Sigma_1$ as $$f=\sum_i \beta_i \sigma_i(w_i x+\theta_i)= \beta_1 \sigma_1(w_1 x+\theta_1)+ ... $$ 
		We can see that the function $$\frac{\sigma([w+h]x + \theta) - \sigma(wx+\theta)}{h} \in \Sigma_1$$ because is a linear combination, where $\beta_1= \frac{1}{h}, \beta_2=\frac{-1}{h}$. \\ \\  By hypothesis, $\sigma \in \mathcal{C}^{\infty}$. By definition of derivative we have
		$$ \frac{d}{dw}\sigma(wx+\theta)= \lim_{h \to 0} \frac{\sigma([w+h]x + \theta) - \sigma(wx+\theta)}{h}  \in \overline{\Sigma_1} %\footnote{$\overline{\Sigma_1}$ denotes the clausure of the set $\Sigma_1$}
		$$
		because the limit of a set belongs to the closure of the set. \\  \\ 
		By the same argument, $$\frac{d^k}{dw^k} \sigma(wx+\theta) \in \overline{\Sigma_1}$$  for all $k\in \mathbb{N}, w,\theta \in \mathbb{R}$.\\ \\ 
		 If we differentiate this expression k times, we obtain 
		$$ \frac{d^k}{dw^k}\sigma(wx+\theta) = \sigma^{(k)}(wx+\theta) \cdot x^{k}$$
		We are going to see that if $\sigma$ is not a polynomial (by hypothesis) then there exists a $\theta_k\in \mathbb{R}$ such that $\sigma^{(k)}(\theta_k)  \neq 0$. To show that, let us assume that does not exist any $ \theta_k \in \mathbb{R}$ such that $\sigma^{(k)}(\theta_k)  \neq 0$. This means that the k-th derivative at every point is 0, i.e. $$\sigma^{(k)}(\theta)=0  \quad \forall \theta \in \mathbb{R} $$
		\noindent  If we integrate this expression, we will have
			$\int \sigma^{(k)}= \int 0$. This implies that $$\sigma^{(k-1)}(x) = C_1$$ for some constant $C_1$, as integrating zero results in a constant. If we integrate again, we have: $$\sigma^{(k-2)}(x) = C_1x + C_2$$ for some constants $C_1$ and $C_2$.
		
		\noindent Continuing this process, we arrive at $$\sigma(x) = C_1x^{k-1} + C_2x^{k-2} + \ldots + C_{k-1}x + C_k$$ for constants $C_1, C_2, \ldots, C_k$. Hence, $\sigma$ is a polynomial of degree $k-1$, which contradicts our assumption that $\sigma$ is not a polynomial. Therefore, there always exists a point where the derivative does not vanish. \\  \\ 
		Thus, we evaluate at the point where the derivative does not vanish, we call it $\theta_k$.
		$$  \sigma^{(k)}(\theta_k) \cdot x^{k}=\frac{d^k}{dw^k}\sigma(wx+\theta) \Bigr|_{w=0, \theta=\theta_k} \in  \overline{\Sigma_1} $$ 
		This implies that $\overline{\Sigma_1}$ contains all polynomials, because the expression $\sigma^{(k)}(\theta_k) x^{k}$ generates all polynomials. By the Weierstrass theorem, we know that the polynomials are dense in $\mathcal{C}(\mathbb{R})$. This concludes that the set $\overline{\Sigma_1}$ contains a set which is dense in  $\mathcal{C}(\mathbb{R})$, therefore $\Sigma_1$ is dense in $\mathcal{C}(\mathbb{R})$.
		
		
	\end{proof}
	
	\begin{lema} % L5: step 5
		If for some $\varphi \in \mathcal{C}^\infty_0 $ we have that $\sigma \ast \varphi $ is not a polynomial, then $\Sigma_1$ is dense in $\mathcal{C}(\mathbb{R})$.
	\end{lema}
	 \begin{proof}
	 From Lemma 3, $\sigma \ast \varphi \in  \overline{\Sigma_1}$ for each $\varphi \in \mathcal{C}^\infty_0$ . It thus follows that, $\sigma \ast \varphi (wx+\theta ) \in  \overline{\Sigma_1}$, for each $ w, \theta \in \mathbb{R}$. Now for $\sigma$ and $\varphi \in \mathcal{C}^\infty_0$, we have that $\sigma \ast \varphi \in  \mathcal{C}^\infty $, see results in distributions \ref{prop:29}.
	 From Lemma 4 applied in $\sigma= \sigma \ast \varphi$, if $\sigma \ast \varphi \in  \mathcal{C}^\infty $, then $\Sigma_1$ dense in $\mathcal{C} (\mathbb{R})$. 
	 \end{proof}
% \subsubsection{{$\Sigma_1$ is dense in $\mathcal{C}(\mathbb{R})$, then $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$ }}
 
 \noindent We will prove that approximating a $\mathcal{C}(\mathbb{R})$ function  with one from the set $\Sigma_1$ implies approximating a function $\mathcal{C}(\mathbb{R}^n)$ from the set $\Sigma_n$. Therefore, it is only necessary to approximate a continuous function. We can see this from the density characterization:

	\begin{lema}  % L6: step 2
			If $\Sigma_1$ is dense in $\mathcal{C}(\mathbb{R})$, then $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$. 
		\end{lema}
	
	\begin{proof} % proof  step 2
			Let $$V:= span\{ f(ax) : a \in \mathbb{R}^n, f \in \mathcal{C}(\mathbb{R}) \}$$ We shall see that $V$ is dense in $\mathcal{C}(\mathbb{R}^n)$.  If we show that $V$ contains the polynomials ( which are dense in $C(\mathbb{R}^n)$ for Weierstrass Theorem) that would be enough. \\ \\  
			\textcolor{red}{!!mirar}
			Let $L(a)$ denote the span of the n rows of $a$ for each $a\in \mathbb{R}^n$. Set $L(R^n) = \cup L(a)$. Let $$H_k^n= \{ \sum c_m s^m \}$$  denote the set of homogeneous polynomials of n variables of total degree k, and $$H^n= \cup_{k=0}^\infty H_k^n$$ the set of all homogeneous polynomials of n variables. \\  \\ 
			Assume that for a given $k\in \mathbb{N}$ no non-trivial $p\in H_k^n \subseteq V$ for all $k\in \mathbb{Z}$, then V contains all polynomials. For that we have V dense in $\mathcal{C}(\mathbb{R}^n)$. Now, we only need to show that $H_k^n \subseteq  V$. SOS
			\\ \\
			Let $g\in \mathcal{C}(\mathbb{R}) $, for any compact subset $K \subset \mathbb{R}^n  $, $V$ dense in $\mathcal{C}(K)$. That is, given $\epsilon >0$, there exist $f_i\in  \mathcal{C}(\mathbb{R})$ and $a_i \in \mathbb{R}^n $    {\scriptsize $i=1,...,k$}  such that
			
			$$ \big| g(x)-\sum_{i=1}^k f_i(a^i \cdot x) \big| < \frac{\epsilon}{2}$$
			for all $x\in K$. We now consider the set of all the points in the compact $K$ multiplied by the vector $a^i$. That is $\{a^i \cdot x | x \in K\}$ $\subseteq[\alpha_i,\beta_i] $ for some finite interval $[\alpha_i,\beta_i]$, $i=1,...,k$. By hipothesis $\Sigma_1 $ dense in $\mathcal{C}(\mathbb{R})$ , specifically $\Sigma_1 $ is dense in $[\alpha_i,\beta_i ]$ $ \, i=1,...,k$. Hence there exist constants $c_{ij}, w_{ij}$ and $\theta_{ij}$, $j=1,...,m_i$, $i=1,...,k$ such that 
			
			$$ \big| f_i(y) - \sum_{j=1}^{m} c_{ij} \sigma(w_{ij}y+ \theta_{ij})\big| < \frac{\epsilon}{2k}$$
			for all $x\in K$. \\ \\
			Therefore, 
			$$ \big| g(x) - \sum_{i=1}^k \sum_{j=1}^m c_{ij} \sigma(w_{ij}(a^i \cdot x) + \theta_{ij})  \big| < \epsilon$$
		\end{proof}
	\noindent We showed that to approximate a $\mathcal{C}(\mathbb{R}^n)$ function we only need to approximate a $\mathcal{C} (\mathbb{R})$ function with the set $\Sigma_1$. 

\section{Proof}
	\begin{proof}~ % proof del teorema

	\begin{enumerate}
		\item[$\Rightarrow$] 
		To prove this implication statement, we aim to show that if $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$, then $\sigma$ is not a polynomial.
		 We will proceed to prove the contrapositive statement, assuming that $\sigma$ is indeed a polynomial, and demonstrate that in this case, $\Sigma_n$ cannot be dense in $\mathcal{C}(\mathbb{R}^n)$. \\ \\ Let $\sigma$ be a polynomial of degree k, then $\sigma(wx+\theta)$ is a polynomial  of degree k for every $w,\theta$. Recall that $$ \Sigma_n = span\{\sigma(w\cdot x + \theta) : w\in \mathbb{R}^n, \theta \in \mathbb{R} \}$$  that is the set of algebraic polynomials of degree at most k. To show that $\Sigma_n$ is not dens in $\mathcal{C}(\mathbb{R}^n)$, for the definition of density, we need to find a function $f(x)\in \mathcal{C}(\mathbb{R}^n)$, $\epsilon > 0$ and $K$ such that  $\| p-f \| > \epsilon$ for all $p$ polynomial of degree k. For example, let $f(x)=cos(x)$, and let $p(x)= \sigma(wx+\theta)$ that has degree at most k. This implies has maximum k roots. We can find a interval where $cos(x)$ has k+1 roots. Therefore, $\Sigma_n$ is not dense in $\mathcal{C}(\mathbb{R}^n)$. 

		\item[$\Leftarrow$]  In order to prove this implication, we need to show that if $\sigma$ is not an algebraic polynomial, then $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$.
		
		
		 By hypothesis $\sigma$ is not a polynomial, by Proposition 1 this implies that $\sigma \ast \varphi$ is not a polynomial. For Lemma 3 we have that $\sigma \ast \varphi \in \overline{\Sigma_1}$. We showed in Lemma 5 that $\sigma \ast \varphi \in \mathcal{C}^\infty$ and for Lemma 4 and  Lemma 5 we have that $\Sigma_1$ is dense in $\mathcal{C}(\mathbb{R})$. Finally, for Lemma 6 $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$.
	\end{enumerate}
\end{proof}


\section{About the theorem}
\subsection{Why does it not contradict the Weierstrass approximation theorem? }
\begin{theorem}(Weierstrass  approximation theorem). 
	Let $f:[a,b]\rightarrow \mathbb{R} $ be a continuous function. Then, there exists polynomials $p_n\in \mathcal{R}[x]$ such that the sequence $(p_n)$ converge uniformly to $f$ on $[a,b]$. 
\end{theorem} 

\begin{corolari}
	The set of polynomial functions $\mathcal{R}^n[x]$ is dense in the space of continuous functions on a compact set $K \subset \mathbb{R}^n$, $\mathcal{C}(K)$. So any continuous function on a compact set can be approximated arbitrarly well by a polynomial. 
\end{corolari}

\noindent The theorem states that: if $\Sigma_n$ is dense in $\mathcal{C}(\mathbb{R}^n)$ then $\sigma$ is not an algebraic polynomial. But why this statment does not contradict the Weierstrass approximation theorem ?
This does not work because $\sigma$ has degree fixed $k$, then any element in the set $\Sigma_n$ has degree at most $k$. Hence, the set $\Sigma_n$ is a finite vector space and can not be dense in $\mathcal{C}(\mathbb{R}^n)$. Not all contiunous functions can be apparoximated with a polynimial of degree fixed, for example: 
(comment per afegir : per exemple una funcio que sigui continua que no es pugui approximar per un polinomi de com a molt grau k , una k tingui grau mes gran que k polinomi de k+1 ?? )


	\cite{leshno1993multilayer}
\end{document}