%%TC:ignore
\documentclass[../../main.tex]{subfiles}

\begin{document}

\chapter*{Acknowledgements} \label{ch:akw} 
\noindent This work marks the end of a beautiful chapter in my life. Since high school, I have been passionate about mathematics. It was the only subject where I truly enjoyed studying, and even though I knew all the exercises on the Euclidean plane by heart, I would repeat them over and over again. However, I always had uncertainty about which career path to choose, which is why I have to thank my high school mathematics teachers Javier Ibañez, Jordi Sorolla, and Jordi Carrillo who encouraged me and instilled their passion for numbers in me. Without them, I wouldn't be here today.\\ \\
\noindent This degree has been an exciting journey filled with effort and sacrifice, where I have been able to share in my love for studying mathematics alongside incredible and highly intelligent people. I am also grateful to all the professors who have taught me throughout my time at the university. And thank you to those who dazzle with passion when explaining, I will always remember them. I would also like to express my heartfelt gratitude to my supervisor, Roberto Rubio. Thank you for guiding and assisting me throughout the development of this thesis and for sharing your passion for mathematics with me.\\ \\
\noindent Finally, I would like to thank my parents and my brother for supporting me through the highs and lows, and for their unconditional love.


\vspace{1cm} \hfill $\mathcal{ACS.}$
\end{document}